### 2012-10-21 thesis/tex/2_background.tex
Translations

Das Thema dieser Arbeit hat sich aus der Situation heraus entwickelt, dass die healthbots der UoA mit sicherheitsmechanismen ausgestattet werden sollen. Die Motivation hierfür, die Roboter mitsamt ihrer Anwendungen und deren technischer Hintergrund werden in Section 1 beschrieben. Auf das VPE, dass die Programmierung dieser Roboter ermöglicht, wird in section 2 eingegangen. Zum Verständnis der sicherstellungskonzepte für sicherheit, auf die diese Arbeit aufbaut, gibt Section 3 eine kurze Einführung in die Welt der funktionalen Sicherheit. In Section 4 werden andere Arbeiten und Programme untersucht, die sich ebenfalls mit Sicherheitüberprüfung beschäftigen.

@@

\section{Robostudio}

@@

\section{Behaviour checking}
TODO: Begriffserklärung: Funktionale Sicherheit

@@

\section{Related work}

>>>>

The subject of this work evolved from the situation, that the healthcare robotic applications of the University of Auckland should be equipped with mechanisms for ensuring safety.
The motivation for it is described in section~\ref{sec:healthbotapplication} as well as the robots, the kind of applications running on them, and their technical background.

The visual programming environment used for the programming of these robots is presented in section~\ref{sec:robostudio}.
For the understanding of safety concepts which this work is based on, a short introduction into the world of functional safety is given in section~\ref{sec:behaviourchecking}. In section~\ref{sec:relatedwork} other works and programs related to this work's topic are examined which also deal with safety aspects.

@@

\section{Robostudio}
\label{sec:robostudio}

@@

\section{Behaviour checking}
\label{sec:behaviourchecking}
TODO: Begriffserklärung: Funktionale Sicherheit

@@

\section{Related work}
\label{sec:relatedwork}

### 2012-10-21 thesis/tex/7_testscenarioandevaluation.tex
Translations

%This expression can now be translated to the visual form as we just have to break down the formula from the outside to the inside. A surrounding \emph{GLOBALLY} encapsulates an \emph{IF} block since it is the substitution for \emph{IMPLIES}. Its first operator is a proposition \emph{'Not taken yet'} whereas the second parameter has to be a \emph{FOLLOWS} block containing a disjunction of two propositions \emph{'Well done!'} and \emph{'Staff notified'}. The resulting visual constraint is shown in figure~\ref{fig:sampleconstraint}.

@@

Ausdruckssärke gleich zu LTL, das heißt, dass lediglich Möglichkeiten nicht ausgedrückt werden können. Zudem gilt eine weitere Einschränkung, dass als bedingungen bisher nur Aussagen der Form ``ist in Zustand x'' verwendet werden können. Da die Validierung der healtbot anwendungen derzeit ausschließlich diesen typ braucht, sind andere Bedingungen wie Stringvergleich oder numerische Gleichheit bisher mit der visuellen Sprache nicht möglich. In Figure~\ref{fig:example_propositions} ist aufgezeigt, wie eine Erweiterung des LTLCreators um weitere Bedingungstypen aussehen könnte.

>>>>

@@

Due to its basing on LTL, the visual language's expressivenes is equivalent to LTL's one of course. More precisely this means any logic formula can be expresssed except potentiality.
Furthermore there is one more limitation in the current visual language with the variety of available proposition operators. The visual language was originally designed for validating healthcare applications where just one kind of proposition is needed: ``currently state x is active''. Thus other propositions such as equations, greater than etc. are not implemented yet, but can be easily extended.
Figure~\ref{fig:example_propositions} depicts how an extention of \emph{LTLCreator} with additional proposition operators could be realised.
